Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-18 papers/clusters.tex
A question for Hogg, and minor char changes

This idea, dubbed ``chemical tagging'', was proposed long ago
\citep{freeman} and is one of the principal motivations for a number
of surveys, most notably \apogee\ \citep{apogee},
\gaiaeso\ \citep{gaiaeso} and \galah\ \citep{galah}.
In order to determine the precise abundance labels for chemical
tagging, these surveys are each measuring high resolution, high
signal-to-noise spectra for hundreds of thousands of stars across the
Galaxy's disk, bulge and halo.

@@

Although undeniably promising---and motivating the 
launch of costly large-scale spectroscopic surveys---%
chemical-tagging as a search technique has yet to be proven in
practice: identifying stars of common birth origin {\it purely} on the
basis of their near-identical abundances patterns, without any
consideration of position or velocity.

@@

>>>>

This idea, dubbed ``chemical tagging'', was proposed long ago
\citep{freeman} and is one of the principal motivations for a number
of surveys, most notably \apogee\ \citep{apogee},
\gaiaeso\ \citep{gaiaeso} and \galah\ \citep{galah}.
In order to determine the precise abundance labels for chemical
tagging, these surveys are each measuring high-resolution, high
signal-to-noise (S/N) spectra for hundreds of thousands of stars across the
Galaxy's disk, bulge and halo.

@@

Although undeniably promising---and motivating the 
launch of costly large-scale spectroscopic surveys---
chemical-tagging as a search technique has yet to be proven in
practice: identifying stars of common birth origin {\it purely} on the
basis of their near-identical abundances patterns, without any
consideration of position or velocity.

@@

% ARC to DWH:   "stand out in a high-dimensional abundance space" -->
%		 	    They'll only stand out in a high-dimensional abundance
% 				space, or a low-dimensional abundance space where those
% 				dimensions are all very orthogonal (e.g., different
% 				nucleosynthetic pathways). Should we add anything to that
%				effect?
